\LARGE Performance Evaluation of Xenomai 3

### 2015-10-20 paper.tex
Fix : author section format issue
Fix : Kernel & Kernel configuration
Kernel : version 3.18 -> 3.14
configuration : NUMA not used, value of HZ?
    power management -> APM & Opportunistic sleep

\author{\large
{\bf Ching-Chun (Jim) Huang }\\
Department of Computer Science and Information Engineering, \\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
\vspace{8mm}
jserv$@$ccns.ncku.edu.tw\\
{\bf Chan-Hsiang Lin}\\
Department of Electrical and Electronic Engineering, National Taiwan University\\
No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% E-MAIL (REQUIRED)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
r04943031$@$ntu.edu.tw
}
\date{}

@@

\subsubsection{Kernel}
A Linux kernel that can be patched with PREEMPT\_RT, Xenomai 2 and Xenomai 3 is needed for the experiment (Xenomai 3 has to run on Linux kernel 3.10 or later versions). We selected Linux 3.18 for our experiment. In some cases when the patches couldn't be successfully applied on the kernel, we tried to resolve the conflicts manually.

\subsubsection{Kernel configuration [ipipe]}
Some of the kernel conﬁguration options may have an impact on real-time latencies. These options include Power Management, especially CPU frequency scaling, value of HZ, NUMA conﬁguration and so on. Additionally, most debug options (Kernel hacking section) lead to increased latencies. We disabled these config options before compilation.

>>>>

\author{\large
{\bf Ching-Chun (Jim) Huang }\\
Department of Computer Science and Information Engineering, \\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
\vspace{8mm}
jserv$@$ccns.ncku.edu.tw\\
{\bf Chan-Hsiang Lin}\\
Department of Electrical and Electronic Engineering, National Taiwan University\\
No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)\\
\vspace{8mm}
r04943031$@$ntu.edu.tw\\
{\bf Che-Kang Wu}\\
Department of Computer Science and Information Engineering, \\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
\vspace{8mm}
an4006048$@$mail.ncku.edu.tw\\
}
\date{}

@@

\subsubsection{Kernel}
A Linux kernel that can be patched with PREEMPT\_RT, Xenomai 2 and Xenomai 3 is needed for the experiment (Xenomai 3 has to run on Linux kernel 3.10 or later versions). We selected Linux 3.14 for our experiment. In some cases when the patches couldn't be successfully applied on the kernel, we tried to resolve the conflicts manually.

\subsubsection{Kernel configuration [ipipe]}
Some of the kernel conﬁguration options may have an impact on real-time latencies. These options include all options under CPU Power Management, APM support, and Opportunistic sleep. Additionally, most debug options in Kernel hacking section lead to increased latencies. Those options are disabled before compilation.
